\begin{thebibliography}{00}
\addcontentsline{toc}{chapter}{Литература}

\bibitem{norwig-ai}
\textbf{Рассел С., Норвиг П.} \textit{Искусственный интеллект: современный подход, 2-е изд.} М. : Вильямс, 2006. 1408 с.

\bibitem{pddl3}
\textbf{Gerevini, A., Long, D.} \textit{Plan constraints and preferences in PDDL3.} Technical Report, Univ. Brescia, Italy, 2005. 12p.


\bibitem{rambo-uml2}
\textbf{Рамбо Дж., Блаха М.} \textit{UML 2.0. Объектно-ориентированное моделирование и разработка, 2-е изд.} СПб. : Питер, 2007

\bibitem{icaps-1}
\textbf{Vaquero T.S., Silva J.R., Beck J.C.} A Brief Review of Tools and Methods for Knowledge Engineering for Planning and Scheduling.
 // Proceedings of the Knowledge Engineering for Planning and Scheduling (KEPS) workshop.
 The 21th International Conference on Automated Planning and Scheduling (ICAPS 2011). Freiburg. Germany. 2011

\bibitem{icaps-2}
\textbf{Vaquero T.S., Costa C., Tonidandel F., Igreja H., Silva J.R., Beck J.C.} Planning and Scheduling Ship Operations on Petroleum Ports and Platforms.
 // Proceedings of the ICAPS 2012 Workshop on Scheduling and Planning Applications (SPARK). 2012. pp. 8-16.

\bibitem{use}
\textbf{Gogolla M., Büttner F., Richter M.}. \textit{USE: A UML-Based Specification Environment for Validating UML and OCL.} Science of Computer Programming, 69:27-34, 2007.

\bibitem{itsimple}
\textbf{Vaquero T. S., Tonaco R. et al.} \textit{itSIMPLE4.0: Enhancing the Modeling Experience of Planning Problems.} Proceedings of the ICAPS 2012 System Demonstration, São Paulo : s.n., 2012. pp. 11-14.

\bibitem{arlou}
\textbf{Арлоу Д., Нейштадт И.} \textit{UML 2 и унифицированный процесс. Практический объектно-ориентированный анализ и проектирование}, 2-е изд. СПб.: Символ-Плюс, 2007

\bibitem{gipo}
\textbf{Simpson R.M.}. \textit{GIPO Graphical Interface for Planning with Objects.} The University of Huddersfield

\bibitem{modisco}
\textbf{Bruneliere H., Cabot J., Dupe G., Madiot F.}. \textit{MoDisco: a Model Driven Reverse Engineering Framework}. Information and Software Technology, 2014.

\bibitem{mal-manz}
\textbf{Малышко В. В., Манжосов А. Н.} Решение задач инженерии знаний средствами объектно-ориентированной инженерии программного обеспечения. // Программные системы и инструменты. Тематический сборник No 13. М.: Изд-во факультета ВМиК МГУ, 2012. С. 44-54.

\bibitem{ocl}
\textbf{Warmer, Kleppe.} \textit{The Object Constraint Language: Getting Your Models Ready for MDA, Second Edition.} Addison-Wesley, 2003.

\bibitem{mofm2t}
Object Management Group MOF Model to Text Transformation Language, v 1.0 2008 \textit{(http://www.omg.org/spec/MOFM2T/1.0/PDF)}

\bibitem{antlr}
\textbf{Terence Parr.} \textit{ The Definitive ANTLR 4 Reference}, 2013. 328p.

\bibitem{pddl4j}
\textbf{Damien Pellier.} PDDL4J: PDDL for Java, 2009 \textit{(https://github.com/gerryai/PDDL4J)}


\end{thebibliography}

\newpage